R code for 'Apparent physiological costs of blood parasite infection in the early-life of a vertebrate host - only in highest infections

### 2022-02-22 MS_physiology_infection.Rmd
Add files via upload

## Plotting mean infection intensity values of nestlings across treatments
## -----------------------------------------------------------------------------
mean_infint = data.frame(
  Sampling_rank = factor(c(rep("1",length(df$Sampling_rank)),as.character(df$Sampling_rank)),levels = c("1","2"),
                         labels  =  c("Pre-treatment","Post-treatment")),
  Infection_intensity = as.numeric(c(as.character(df$Infection_intensity.1),as.character(df$Infection_intensity))),
  Treatment = factor(c(as.character(rep(df$Treatment,2))),levels  =  c("Control","Malarone")))

## Figure 2b
## -----------------------------------------------------------------------------
treatment_meaninf_changes = ggplot(mean_infint) +
  aes(Sampling_rank, Infection_intensity, group = Treatment) +
  geom_vline(xintercept  =  "Pre-treatment", linetype = "dashed", color = 'darkgrey') +
  geom_vline(xintercept = "Post-treatment", linetype = "dashed", color = 'darkgrey') +
  labs(y = "Mean infection intensity") +
  geom_point(aes(colour = Treatment),position = position_jitterdodge(jitter.height  =  0.1)) +
  stat_summary(fun = mean, geom = "line",size = 2,color = c("lightgrey","black","black","lightgrey")) +
  stat_summary(fun = mean, geom = "point",size = 5) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.04, size = 2) + 
  scale_color_manual(values = c("lightgrey","black")) + 
  theme_classic() + 
  theme(axis.title.x = element_blank(),
        legend.text = element_text(size = 16),
        legend.title = element_text(size = 16),
        axis.title.y = element_text(size = 18, margin =  unit(c(0, 3, 0, 0), "mm")),
        axis.text = element_text(size = 16),
        plot.margin = unit(c(0,0,0,30), "pt"))

## Panel wrapping Fig2 a & b:
## ----------------------------------------------------------------------------- 
Fig2 <- treatment_prevalence_changes + 
  treatment_meaninf_changes +
  plot_annotation(tag_levels = 'A') + 
  theme(plot.tag = element_text(size = 16, face = "bold"))
ggsave(Fig2,filename = "./Figs/efficiency_malarone.png",units = "px", width = 6000, height = 3000)

@@

## Create Table S1
## -----------------------------------------------------------------------------
tab_model(
  lm_d1,lm_d2,lm_d3,lm_d4,
  show.reflvl = T,
  show.ci50 = T ,
  show.stat = T,
  string.stat = "t",
  pred.labels = c("Intercept","Treatment [Malarone]"),
  dv.labels = c("Breathing rate","Body temperature", "\U0394 Body condition","Growth rate"),
  file = "./Tables/Physiological_parameters_in_decreasing_control_treated.html")
```

@@

```{r}
## Figure 4 
## -----------------------------------------------------------------------------
fig4 <- gg1_pred + gg2_pred + gg3_pred + gg4_pred + plot_annotation(tag_levels = 'A') & 
  theme(plot.tag = element_text(size = 16, face = "bold"))
ggsave(fig4,filename = "./Figs/predicted_physio_param_infection_stages.png",units = "px", width = 3700, height = 3700)

# Table 3
## -----------------------------------------------------------------------------
sjPlot::tab_model(
  lmer_br,lmer_bt,lmer_bc,lmer_gr,
  show.ci50 = T ,
  show.stat = T,
  string.stat = "t",
  df.method = "kr",
  dv.labels = c("Breathing rate","Body temperature","\U0394 Body condition","Growth rate"),
  file = "./Tables/Table_results_lmer_physiological_parameters_p.val_kr.html")
```

@@

ggsave(fig5,filename = "./Figs/predicted_physio_param_infection_intensities.png",units = "px", width = 3700, height = 3700)

@@

sjPlot::tab_model(lmer_br_para,lmer_bt_para,lmer_bc_para,lmer_gr_para,
                  show.ci50 = T ,
                  show.stat = T,
                  string.stat = "t",
                  p.val = "kr",
                  dv.labels = c("Breathing rate","Body temperature","\U0394 Body condition","Growth rate"),
                  file = "./Tables/table_results_parasitemia_lmer_physiological_parameters_p.val_kr.html")

@@

```{r, warning=F,message=F}

@@

ggsave(g,filename = "./Figs/delta_body_condition_to_parasitemia_second.png",units = "px", width = 3700, height = 2800)
```

@@

ggsave(figs1,filename = "./Figs/observed_physio_param_infection_stages.png",units = "px", width = 3500, height = 3800)

@@

ggsave(figs2,filename = "./Figs/observed_physio_param_parasitemia.png",units = "px", width = 3500, height = 3800)

@@

ggsave(figs3,filename = "./Figs/effect_sizes_param_stages.png",units = "px", width = 3500, height = 3800)

@@

ggsave(figs4,filename = "./Figs/effect_sizes_param_intensities.png",units = "px", width = 3500, height = 3800)
```
## Estimating measurment error of body temperature

>>>>

## Plotting mean infection intensity values of nestlings across treatments
## -----------------------------------------------------------------------------
mean_infint = data.frame(
  Sampling_rank = factor(c(rep("1",length(df$Sampling_rank)),as.character(df$Sampling_rank)),levels = c("1","2"),
                         labels  =  c("Pre-treatment","Post-treatment")),
  Infection_intensity = as.numeric(c(as.character(df$Infection_intensity.1),as.character(df$Infection_intensity.2))),
  Treatment = factor(c(as.character(rep(df$Treatment,2))),levels  =  c("Control","Malarone")))

## Figure 2b
## -----------------------------------------------------------------------------
treatment_meaninf_changes = ggplot(mean_infint) +
  aes(Sampling_rank, Infection_intensity, group = Treatment) +
  geom_vline(xintercept  =  "Pre-treatment", linetype = "dashed", color = 'darkgrey') +
  geom_vline(xintercept = "Post-treatment", linetype = "dashed", color = 'darkgrey') +
  labs(y = "Mean infection intensity") +
  geom_point(aes(colour = Treatment),position = position_jitterdodge(jitter.height  =  0.1))+
  stat_summary(fun = mean, mapping = aes(group=Treatment), geom = "line",size = 2,color = c("lightgrey","black","black","lightgrey"))+ 
  stat_summary(fun = mean, geom = "point",size = 5) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.04, size = 2) + 
  scale_color_manual(values = c("lightgrey","black")) + 
  theme_classic() + 
  theme(axis.title.x = element_blank(),
        legend.text = element_text(size = 16),
        legend.title = element_text(size = 16),
        axis.title.y = element_text(size = 18, margin =  unit(c(0, 3, 0, 0), "mm")),
        axis.text = element_text(size = 16),
        plot.margin = unit(c(0,0,0,30), "pt"))

## Panel wrapping Fig2 a & b:
## ----------------------------------------------------------------------------- 
Fig2 <- treatment_prevalence_changes + 
  treatment_meaninf_changes +
  plot_annotation(tag_levels = 'A') + 
  theme(plot.tag = element_text(size = 16, face = "bold"))
ggsave(Fig2,filename = "./Figs/Fig2_efficiency_malarone.png",units = "px", width = 6000, height = 3000)

@@

## Create Table S1
## -----------------------------------------------------------------------------
tab_model(
  lm_d1,lm_d2,lm_d3,lm_d4,
  show.reflvl = T,
  show.ci50 = T ,
  show.stat = T,
  string.stat = "t",
  pred.labels = c("Intercept","Treatment [Malarone]"),
  dv.labels = c("Breathing rate","Body temperature", "\U0394 Body condition","Growth rate"),
  file = "./Tables/TableS1_Physiological_parameters_in_decreasing_control_treated.html")
```

@@

```{r}
## Figure 4 
## -----------------------------------------------------------------------------
fig4 <- gg1_pred + gg2_pred + gg3_pred + gg4_pred + plot_annotation(tag_levels = 'A') & 
  theme(plot.tag = element_text(size = 16, face = "bold"))
ggsave(fig4,filename = "./Figs/Fig4_predicted_physio_param_infection_stages.png",units = "px", width = 3700, height = 3700)

# Table 3
## -----------------------------------------------------------------------------
sjPlot::tab_model(
  lmer_br,lmer_bt,lmer_bc,lmer_gr,
  show.ci50 = T ,
  show.stat = T,
  string.stat = "t",
  df.method = "kr",
  dv.labels = c("Breathing rate","Body temperature","\U0394 Body condition","Growth rate"),
  file = "./Tables/Table3_results_lmer_physiological_parameters_p.val_kr.html")
```

@@

ggsave(fig5,filename = "./Figs/Fig5_predicted_physio_param_infection_intensities.png",units = "px", width = 3700, height = 3700)

@@

sjPlot::tab_model(lmer_br_para,lmer_bt_para,lmer_bc_para,lmer_gr_para,
                  show.ci50 = T ,
                  show.stat = T,
                  string.stat = "t",
                  p.val = "kr",
                  dv.labels = c("Breathing rate","Body temperature","\U0394 Body condition","Growth rate"),
                  file = "./Tables/Table4_results_parasitemia_lmer_physiological_parameters_p.val_kr.html")

@@

```{r, warning=F,message=F}
# Results presented in Table 2

@@

ggsave(g,filename = "./Figs/Fig3_delta_body_condition_to_parasitemia_second.png",units = "px", width = 3700, height = 2800)
```

@@

ggsave(figs1,filename = "./Figs/FigS1_observed_physio_param_infection_stages.png",units = "px", width = 3500, height = 3800)

@@

ggsave(figs2,filename = "./Figs/FigS2_observed_physio_param_parasitemia.png",units = "px", width = 3500, height = 3800)

@@

ggsave(figs3,filename = "./Figs/FigS3_effect_sizes_param_stages.png",units = "px", width = 3500, height = 3800)

@@

ggsave(figs4,filename = "./Figs/FigS4_effect_sizes_param_intensities.png",units = "px", width = 3500, height = 3800)
```
## Estimating measurment error of body temperature
